The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-22 paper.tex
Added start of 3C section

We will use the existing sonority scale given in \ref{standardsonorityscale}, with a small modification. Chaha has a bilabial approximant represented by [\textipa{B}] (more precisely, \textipa{\|`B}) \citep[15]{banksira.2000} that is not as sonorous as /r/, whose realisation is tap-like \citep[181]{taranto.2001}. The justification for /\textipa{B}/ being less sonorous than /r/ is largely empirical, based on the epenthetic behaviour of clusters containing this sonorant \citep{405}{rose.2000}, data for which will be presented later in this paper. I will specify its sonority as an intermediate 3.5, under the sonority of 4 for liquids in general.

@@

\begin{center}
\begin{tabular}{ccccccccccccc}
 V & $>$ & w j & $>$ & r & $>$ & \textipa{B} & $>$ & m n & $>$ & f s z x & $>$ & t t' k k' d g \\
 vowels & & glides & & liquids & &   & & nasals & & fricatives & & stops \\
    V   & &    G   & &    R    & & \textipa{B} & & N & & F & & T \\
    6   & &    5   & &    4    & &    3.5      & & 3 & & 2 & & 1 \\
\end{tabular}
\end{center}
\subsection{CC clusters}

@@

>>>>

We will use the existing sonority scale given in \ref{standardsonorityscale}, with a small modification. Chaha has a bilabial approximant represented by [\textipa{B}] (more precisely, \textipa{\|`B}) \citep[15]{banksira.2000} that is not as sonorous as /r/, whose realisation is tap-like \citep[181]{taranto.2001}. The justification for /\textipa{B}/ being less sonorous than /r/ is largely empirical, based on the epenthetic behaviour of clusters containing this sonorant \citep[405]{rose.2000}, data for which will be presented later in this paper. I will specify its sonority as an intermediate 3.5, under the sonority of 4 for liquids in general.

@@

\begin{center}
\begin{tabular}{ccccccccccccc}
 V & $>$ & w j & $>$ & r & $>$ & \textipa{B} & $>$ & m n & $>$ & f s z x & $>$ & t t' k k' d g \\
 vowels & & glides & & liquids & &   & & nasals & & fricatives & & stops \\
    V   & &    G   & &    R    & & \textipa{B} & & N & & F & & T \\
    6   & &    5   & &    4    & &    3.5      & & 3 & & 2 & & 1 \\
\end{tabular}
\end{center}

\subsection{Data: CC clusters}

@@

  The variability therefore lies in (1) whether epenthesis between obstruents is possible (between stops, between a stop and a fricative, and between two fricatives), and (2) whether [r]-sonorant can be broken up by epenthesis or not.
  The variable setting of these two options corresponds to four attested idiolects:

  \ex. \label{idiolects} The four idiolects:
       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \b. \label{idiolectb} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
       \c. \label{idiolectc} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]

The evidence of the epenthetic behaviour of coda clusters accords with the {\sc Sonority Angle} prediction that RN should be the most likely to epenthesise out of the falling sonority clusters.

\subsection{Data: CCC clusters}

Triconsonantal clusters are always broken up as [CC\textipa{1}C] or [C\textipa{1}CC]. The sources
of CCC clusters in Chaha are the 3rd singular masculine conjugation of the jussive form of
triliteral verbs, which have the underlying form /j\textipa{@}-\underline{CCC}-o/, and
the 3rd singular masculine conjugation of the passive/reflexive form of quadriliteral verbs,
which have the underlying form /j-\underline{t-CC}aCaC/.

As with coda clusters, there is considerable variability in epenthetic positioning between idiolects.
In what follows, I assume that the primary forms presented in Section 4.3 of \citet{rose.2000} are preferred forms, and the secondary variants presented in Section 5 are less preferred.
